%=========================================================
\chapter{Bibliografía}

\begin{description}
	
		\item[\hypertarget{b01}{[1]}] Rui, K. Butler, G. (2003, April 21). Refactoring use case models: the metamodel [Online]. Available: https://dl.acm.org/citation.cfm?id=783140
		
		\item[\hypertarget{b02}{[2]}] Shuang, L. Sun, L. (2014, September 19). Automatic early defects detection in use case documents [Online]. Available: https://dl.acm.org/citation.cfm?id=2642969
		
		\item[\hypertarget{b03}{[3]}] 
		J. Lee. (1999, August). Analyzing user requirements use cases a goal driven approach. [Online]. Avaible: https://ieeexplore.ieee.org/document/776956
		
		\item[\hypertarget{b04}{[4]}]  L. Julijana. (2007, August). “Information Systems Modeling with Use Cases” IEEE Computer [Online]. Available:
		https://ieeexplore.ieee.org/document/4283759
		
		\item[\hypertarget{b05}{[5]}] Jason Gorman, J. G. (2007, 9 marzo). 10 Common Use Case Pitfalls. Recuperado 23 abril, 2018,  [Online]. Available: http://codemanship.co.uk/parlezuml/blog/?postid=364
		
		\item[\hypertarget{b06}{[6]}] Susan Lilly [2002, August]. “Use Case Pitfalls: Top 10 Problems from Real Projects Using Use Cases” [Online]. Avaible: https://ieeexplore.ieee.org/document/787547
		
		\item[\hypertarget{b07}{[7]}] Pressman, Roger. (2010). Ingenieria de Software. Un enfoque práctico / 7 ED.(777 páginas). USA: Mcgraw-Hill Interamericana.
		
		\item[\hypertarget{b08}{[8]}] B. Imran S. and H. Irfan, "UCD-generator - a LESSA application for use case design - IEEE Conference Publication", Ieeexplore.ieee.org, 2007. [Online]. Available: https://ieeexplore.ieee.org/document/4381333.
		
		\item[\hypertarget{b09}{[9]}] G. Booch, J. Rumbaugh, I. Jacobson, J. García Molina and J. Saez Martínez, El lenguaje unificado de modelado, 2nd ed. Madrid: Pearson Educación, 2010.
		
		\item[\hypertarget{b10}{[10]}] D. West, "Use Cases Considered Valuable (but Optional) For Lean/Agile Requirements Capture", InfoQ, 2010. [Online]. Available: https://www.infoq.com/news/2009/02/Use-Cases-Valuable-But-Optional. 
		
		\item[\hypertarget{b11}{[11]}] D. González, "Industria Mexicana del Software. Un estudio en cifras.", SG Buzz, 2005. [Online]. Available: https://sg.com.mx/revista/9/industria-mexicana-cifras. [Accessed: 20- Apr- 2019].
		
		\item[\hypertarget{b12}{[12]}] J. Gómez, "Métodos de Medición en Puntos Función (I): IFPUG FPA", El Laboratorio de las TI, 2014. [Online]. Available: https://www.laboratorioti.com/2013/01/16/metodos-de-medicion-en-puntos-funcion-i/. 
\end{description}